|

### 2025-05-04 doc/paper.qmd
signature upd
Added abstract, acknowledgments, list of abbreviations

bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
    lof: true  # Enables List of Figures
    lot: true  # Enables List of Tables
    include-before-body: 
      text: |
        \pagenumbering{Roman}
    include-after-body:
      - declaration.tex

@@

# List of Abbreviations
\setlength{\parindent}{0em}
**BHR**: Buy-and-Hold Returns   
**CRSP**: Center for Research in Security Prices  
**DS**: Datastream  
**IDE**: Integrated Development Environment  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**WRDS**: Wharton Research Data Services  
**WSCP**: Worldscope

\setlength{\parindent}{4em}

\pagebreak
\pagenumbering{arabic}

>>>>

bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
    lof: true  # Enables List of Figures
    lot: true  # Enables List of Tables
    include-before-body: 
    - acknowledgements.tex
    - abstract.tex
    - abbreviations.tex
    include-after-body:
      - declaration.tex

@@

\pagenumbering{arabic}
